R for Clinical Study Reports and Submission

### 2021-10-05 index.Rmd
create CNAME file

documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes

---

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
options(dplyr.summarise.inform = FALSE)
```

>>>>

documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
---

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
options(dplyr.summarise.inform = FALSE)
file.copy("static/CNAME", "_book", overwrite = TRUE)
```
